Stochastic Variance-Reduced Policy Gradient

### 2018-02-08 svrpg.tex
Modified experiments in appendices and cited precup in section 5.2

\subsection{Normalized Importance Sampling}\label{sec:prac}
As mentioned in Section~\ref{sec:stopping}, importance weights are an additional source of variance. A standard way to cope with this issue is self-normalization.
This technique can reduce the variance of the importance weights at the cost of introducing some bias. Whether the trade-off is advantageous depends on the specific task.  
Introducing self-normalization in the context of our algorithm, we switch from Eq.~\eqref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) = \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
In Section \ref{sec:exp} we show some cases in which self-normalization provides a performance improvement.
\todomat{add reference, maybe just Precup}

@@

\centering
\begin{tabular}{| l | c  c  c |}
	\hline	
	& Cart-Pole & Swimmer & Half Cheetah \\
	\hline
	State space dimension  & 4 & 13 & 20 \\
	Control space dimension & 1 & 2 & 6 \\
	NN Hidden layers & 8 & 32x32 & 32x32 \\
	Learning rate & $10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
	Snapshot trajectories & 100 & 100 & 100 \\
	Sub-iterations trajectories/GPOMDP batch & 10 & 10 & 10 \\
	Max sub-iterations & 50 & 20 & 20 \\
	Trajectories lengths& 500 & 500 & 500 \\
	Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
	Total trajectories& 10000 & 20000 & 50000 \\
	\hline  
\end{tabular}

>>>>

\subsection{Normalized Importance Sampling}\label{sec:prac}
As mentioned in Section~\ref{sec:stopping}, importance weights are an additional source of variance. A standard way to cope with this issue is self-normalization \citep{precup2000eligibility}.
This technique can reduce the variance of the importance weights at the cost of introducing some bias. Whether the trade-off is advantageous depends on the specific task.  
Introducing self-normalization in the context of our algorithm, we switch from Eq.~\eqref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) = \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
In Section \ref{sec:exp} we show some cases in which self-normalization provides a performance improvement.

@@

\centering
\begin{tabular}{| l | c  c  c |}
	\hline	
	& Cart-Pole & Swimmer & Half Cheetah \\
	\hline
	State space dimension  & 4 & 13 & 20 \\
	Control space dimension & 1 & 2 & 6 \\
	NN Hidden layers & 8 & 32x32 & 32x32 \\
	Learning rate & $10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
	Snapshot trajectories & 100 & 100 & 100 \\
	Sub-iterations trajectories & 10 & 10 & 10 \\
	Max sub-iterations & 50 & 20 & 20 \\
	Trajectories lengths& 500 & 500 & 500 \\
	Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
	Total trajectories& 10000 & 20000 & 50000 \\
	\hline  
\end{tabular}
